Dynein walks like an Imperial AT-ST

### 2017-12-05 papers/paper/paper.tex
clean up figures and add new color plot to paper

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-trajectory-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
\caption{Histogram of duration of steps taken by model.}
\label{fig:timehist}
\end{figure*}

@@

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-1-cryoem}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-1-superimposed}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-1-model}
   \label{fig:explengths}
 \end{minipage}
 %
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-2-cryoem}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-2-superimposed}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-2-model}
   \label{fig:explengths}
 \end{minipage}
\caption{\textbf{Model schematic superimposed on cryo-EM images of native dynein.} Native cryo-EM images of the full dimerized dynein complex composed of light, intermediate and heavy chains, from \cite{nativestructure}. Model schematics are superimposed for illustrative purpose; shown angles to not represent expected \textit{in vivo} equilibria. Schematics are shown docked to a microtubule for illustrative purposes.}
\label{fig:modelparams}
\end{figure}

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-prestroke}
   \label{fig:prestrokeangle}
 \end{minipage}%
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-poststroke}
   \label{fig:poststrokeangle}
 \end{minipage}
 %
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-binding-angle}
   \label{fig:bindingangle}
 \end{minipage}
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=0.5\linewidth]{figures/schematic-full}
   \label{fig:allangles}
 \end{minipage}
\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}

>>>>

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-trajectory-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
\caption{Histogram of duration of steps taken by model.}
\label{fig:timehist}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
\caption{Histogram of duration and length of steps taken by model.}
\label{fig:timehist}
\end{figure}

@@

\begin{figure}%[tbhp]
  \centering
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}

   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
   \caption{\textbf{Model schematic superimposed on cryo-EM images of
       native dynein.} Native cryo-EM images of the full dimerized
     dynein complex composed of light, intermediate and heavy chains,
     from \cite{nativestructure}. Model schematics are superimposed
     for illustrative purpose; shown angles to not represent expected
     \textit{in vivo} equilibria. Schematics are shown docked to a
     microtubule for illustrative purposes.}
   \label{fig:modelparams}
\end{figure}

\begin{figure}%[tbhp]
  \centering
\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
    dynein heavy chains superimposed with model motor angles, both
    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
    MT with model binding angle superimposed, from
    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
    bound to an MT with model superimposed, from
    \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}

See schematic in Figure~\ref{fig:modelangles}.
